\paperTitle

### 2014-05-17 doc/icml2014/directed.tex
Updated figures
Updated references to learnclique, directed in the exclusive-views section

\begin{figure}
  \centering
  \subfigure[Three-view mixture model] {
    \includegraphics[width=0.45\columnwidth]{figures/three-view.pdf}
    \label{fig:three-view}
  }
  \subfigure[Exclusive views]{
    \includegraphics[width=0.45\columnwidth]{figures/exclusive-views.pdf}
    \label{fig:exclusive-views}
  }

  \caption{(a) The canonical three-view mixture model can be estimated consistently
  using tensor factorization \citep{anandkumar13tensor}.
  (b) An example of exclusive views for a bi-dependent subset $S$.
  }
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Estimating hidden clique marginals}

@@

\algorithmref{learnclique} summarizes the procedure, \LearnMarginals.
Given $Z_S$, the conditional probability tables for $S$ can easily be
obtained via renormalization.
\begin{theorem}[Hidden marginals from exclusive views]
If $S \subseteq \bx$ is a subset of hidden variables with the exclusive views property,
then \algorithmref{learnclique} recovers the marginals $Z_S = \Pr(\bh_S)$.
\end{theorem}

@@

% Define bidependent
First, define the notion of a bidependent set (in analogy with biconnected component),
in which conditionining on one variable does not break the set apart:
\begin{definition}[Bidependent set]
Given a graphical model $\sG$, we say that a subset of nodes $S$ is \emph{bidependent} if
conditioned on any $a \in S$, there is an active trail between any other two nodes $b,c \in S$.
\end{definition}
Note that all cliques are bidependent, but bidependent sets can have more conditional independences.
this will be important for pseudolikliehood in \sectionref{pseudolikelihood}.

@@

%Note that bottlenecks provide three views, which is important for condition (ii) of
%\definitionref{exclusive-views}, only two is required for condition (i).
With this lemma in place, we present our full algorithm, $\LearnMarginals$,
in \algorithmref{directed}.

@@

Our method also extends directly to case in which the observed variables
  are real-valued, while the hidden variables remain discrete. 
In this setting, the tensor factorization method of
  \citet{anandkumar13tensor} recovers the expected conditional means,
  $\mu_{vi} \eqdef \E(x_v | h_i) \in \Re^{d \times k}$ for each observed variable $x_v$ and
  hidden variable $h_i$.
\algorithmref{learnclique} and \algorithmref{directed} still apply and allow
  us to recover clique marginals $Z_\sC$.
%  \todo{make this a footnote if running out of space}
% PL: don't understand this comment
%In this case, we only require that the hidden variables in distinct
  %cliques share parameters.

>>>>

\begin{figure}
  \centering
  \subfigure[Bottleneck] {
    \includegraphics[width=0.35\columnwidth]{figures/three-view.pdf}
    \label{fig:three-view}
  }
  \subfigure[Exclusive views]{
    \includegraphics[width=0.45\columnwidth]{figures/exclusive-views.pdf}
    \label{fig:exclusive-views}
  }

  \caption{(a) A bottleneck can be estimated consistently
  using tensor factorization \citep{anandkumar13tensor}.
  (b) An example of exclusive views for a bi-dependent subset $S$.
  }
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Estimating hidden subset marginals}

@@

\algorithmref{learnMarginals} summarizes the procedure, \LearnMarginals.
Given $Z_S$, the conditional probability tables for $S$ can easily be
obtained via renormalization.
\begin{theorem}[Hidden marginals from exclusive views]
If $S \subseteq \bx$ is a subset of hidden variables with the exclusive views property,
then \algorithmref{learnMarginals} recovers the marginals $Z_S = \Pr(\bh_S)$.
\end{theorem}

@@

% Define bidependent
First, define the notion of a bidependent set (in analogy with biconnected component),
in which conditionining on one variable does not break the set apart:
\begin{definition}[Bidependent set]
Given a graphical model $\sG$, we say that a subset of nodes $S$ is \emph{bidependent} if
conditioned on any $a \in S$, there is an active trail between any other two nodes $b,c \in S$.
\end{definition}
Note that all cliques are bidependent, but bidependent sets can have more conditional independences.
This will be important for pseudolikliehood in \sectionref{pseudolikelihood}.

@@

%Note that bottlenecks provide three views, which is important for condition (ii) of
%\definitionref{exclusive-views}, only two is required for condition (i).
% With this lemma in place, we present our full algorithm, $\LearnMarginals$,
% in \algorithmref{learnMarginals}.

@@

Our method also extends directly to case in which the observed variables
  are real-valued, while the hidden variables remain discrete. 
In this setting, the tensor factorization method of
  \citet{anandkumar13tensor} recovers the expected conditional means,
  $\mu_{vi} \eqdef \E(x_v | h_i) \in \Re^{d \times k}$ for each observed variable $x_v$ and
  hidden variable $h_i$.
\algorithmref{learnMarginals} % and \algorithmref{directed} 
still applies and allow us to recover clique marginals $Z_\sC$.
%  \todo{make this a footnote if running out of space}
% PL: don't understand this comment
%In this case, we only require that the hidden variables in distinct
  %cliques share parameters.
